---
title: "salmon_group19"
author: "Alicia Fennell"
date: "2/2/2021"
output: html_document 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Overview 

- An engaging image (with caption, including photo credit) that is relevant to the dataset
- A brief summary (3 - 4 sentences) of the dataset, and what is included in this “report”
- A map of the fish ladder location (you can make this in R on your own, or include an existing map appropriately licensed, with attribution)
- A professionally formatted data citation


## Making tabs (some type of title) {.tabset}

### Time series

Need to figure out how to fold code 

```{r}

## Read in packages 
library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(tsibble)

## Read in the data, keep only the columns of interest, replace "NA" with 0, and clean names
fish_af <- read.csv(here("data", "willamette_fish_passage.csv")) %>% 
  select("Date", "Coho", "Jack.Coho", "Steelhead") %>% 
  mutate_all(~replace(., is.na(.), 0)) %>% 
  clean_names()
  
## Convert to tsibble 
fish_ts <- fish_af %>% 
  mutate(date = lubridate::mdy(date)) %>% 
  as_tsibble(key = NULL, index = date)

## Plot the time series data
ggplot() +
  geom_line(data = fish_ts, aes(x = date, y = coho)) +
  labs(x = "Date",
       y = "Number of Coho")

## Make data frames for each fish by monthyears  
coho_month <- fish_ts %>% 
  index_by(yr_mo = ~yearmonth(.)) %>% 
  summarize(monthly_mean_coho = mean(coho, na.rm = TRUE))

jack_month <- fish_ts %>% 
  index_by(yr_mo = ~yearmonth(.)) %>% 
  summarize(monthly_mean_jack = mean(jack_coho, na.rm = TRUE))

steel_month <- fish_ts %>% 
  index_by(yr_mo = ~yearmonth(.)) %>% 
  summarize(monthly_mean_steel = mean(steelhead, na.rm = TRUE))
```


```{r}
## Plot time series fish runs 
ggplot() +
  geom_line(data = coho_month,
       aes(x = yr_mo,
           y = monthly_mean_coho,
           colour = "Coho"),
        alpha = 0.7,
        size = 1.2) +
  geom_line(data = jack_month,
       aes(x = yr_mo,
           y = monthly_mean_jack,
           colour = "Jack Coho"),
       alpha = 0.7,
       size = 1.2) +
  geom_line(data = steel_month,
       aes(x = yr_mo,
           y = monthly_mean_steel,
           colour = "Steelhead"),
       alpha = 0.7,
      size = 1.2) +
  labs(x = "Month and Year",
       y = "Number of Fish",
       title = "Adult Passage of Coho, Jack Coho, and Steelhead at Willamette Falls") +
  theme_minimal() +
  scale_colour_manual(values = c("dodgerblue4", "darkorchid4", "springgreen4")) 

  
```

- bullet points summarizing 
- trends... 

### Tab 2 testing 

### Tab 3 woohooo!